Contracts for unions and intersections are hard for Nickel

### 2021-04-27 paper.tex
Update paper.tex
Co-authored-by: Teodoro Freund <tfreund95@gmail.com>
Squashed commit of the following:
commit 29c6e1d668c9b945b186b4e9b92039dd799eb432
Merge: 7dd0b8b eb71bb3
Author: Yann Hamdaoui <yann.hamdaoui@gmail.com>
Date:   Tue Apr 20 16:12:24 2021 +0200

    Merge pull request #1 from tweag/motivations-background

    Background and motivations

commit eb71bb33aeee9be1b5b7441fbaea85295be737c7
Author: Yann Hamdaoui <yann.hamdaoui@gmail.com>
Date:   Tue Apr 20 16:03:11 2021 +0200

    Update paper.tex

    Co-authored-by: Teodoro Freund <tfreund95@gmail.com>

commit 1e89c5e092da83d33c8fa

@@

\section*{Introduction}
Intro

@@

Our aim is that writing simple Nickel feels as easy as writing JSON or YAML.
Unlike JSON, though, Nickel anticipates large configurations by being both
programmable and typed. In the configuration setting, there is a singular
dilemma with respect to typing: since a program is run on fixed inputs and is
expected to terminate, any relevant type error will show up at evaluation.  Why
bother with the complexity of a static type system? On the other hand, more and
more software systems offload complexity to configurations, in particular with
the infrastructure as code paradigm prevailing today in cloud deployment. When
the complexity of a codebase grows, static types becomes attractive again.  For
reusable code — that is, library functions —, static types are specifically
adapted, and bring all the usual benefits of early error detection, code
robustness, better code structure, documentation, and so on.

@@

\subsection{Unions types}
\color{red}Goals of the section

@@

$(A -> B) /\ (C -> D) ~ (A \/ C) -> (B \/ D)$
$(A \/ B) -> C ~ (A -> C) /\ (B -> C)$

@@

>>>>

%%%%%%%%%%%%%%%%% Editing marks %%%%%%%%%%%%%%%%%

  % TOGGLE ME to turn off all the commentary:
  \InputIfFileExists{no-editing-marks}{
    \def\noeditingmarks{}
  }

  \usepackage{xargs}
  \usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
  % ^^ Need for pgfsyspdfmark apparently?
  \ifx\noeditingmarks\undefined
      \setlength{\marginparwidth}{1.2cm} % A size that matches the new PACMPL format
      \newcommand{\Red}[1]{{\color{red}{#1}}}
      \newcommand{\newaudit}[1]{{\color{blue}{#1}}}
      \newcommand{\note}[1]{{\color{blue}{\begin{itemize} \item {#1} \end{itemize}}}}
      \newenvironment{alt}{\color{red}}{}

      \newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
      \newcommandx{\info}[2][1=]{\todo[linecolor=green,backgroundcolor=green!25,bordercolor=green,#1]{#2}}
      \newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
      \newcommandx{\inconsistent}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=red,#1]{#2}}
      \newcommandx{\critical}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=red,#1]{#2}}
      \newcommand{\improvement}[1]{\todo[linecolor=pink,backgroundcolor=pink!25,bordercolor=pink]{#1}}
      \newcommandx{\resolved}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} % use this to mark a resolved question
  \else
  %    \newcommand{\Red}[1]{#1}
      \newcommand{\Red}[1]{{\color{red}{#1}}}
      \newcommand{\newaudit}[1]{#1}
      \newcommand{\note}[1]{}
      \newenvironment{alt}{}{}
  %    \renewcommand\todo[2]{}
      \newcommand{\unsure}[2][1=]{}
      \newcommand{\info}[2][1=]{}
      \newcommand{\change}[2]{}
      \newcommand{\inconsistent}[2]{}
      \newcommand{\critical}[2]{}
      \newcommand{\improvement}[1]{}
      \newcommand{\resolved}[2]{}
  \fi

%%%%%%%%%%%%%%%%% /Editing marks %%%%%%%%%%%%%%%%%

@@

\section*{Introduction}
Intro\unsure{todo}

@@

Our aim is that writing simple Nickel feels as easy as writing JSON or YAML.
Unlike JSON, though, Nickel anticipates large configurations by being both
programmable and typed. In the configuration setting, there is a singular
dilemma with respect to typing: since a program is run on fixed inputs and is
expected to terminate, any relevant type error will show up at evaluation.  Why
bother with the complexity of a static type system? On the other hand, more and
more software systems offload complexity to configurations, in particular with
the infrastructure as code paradigm prevailing today in cloud deployment. When
the complexity of a codebase grows, static types become attractive again.  For
reusable code — that is, library functions —, static types are specifically
adapted, and bring all the usual benefits of early error detection, code
robustness, better code structure, documentation, and so on.

@@

\subsection{Union types}
\color{red}Goals of the section

@@

$$(A -> B) \cap (C -> D) \sim (A \cup C) -> (B \cup D)$$
$$(A \cup B) -> C \sim (A -> C) \cap (B -> C)$$

@@

\section{Challenges}
\input{challenges}
